% -----------------------------------------------
% Template for ISMIR Papers
% 2017 version, based on previous ISMIR templates

% Requirements :
% * 6+n page length maximum
% * 4MB maximum file size
% * Copyright note must appear in the bottom left corner of first page
% * Clearer statement about citing own work in anonymized submission
% (see conference website for additional details)
% -----------------------------------------------

\documentclass{article}
\usepackage{ismir,amsmath,cite,url}
\usepackage{graphicx}
\usepackage{color}
\usepackage{microtype}


% Title.
% ------
\title{Automatic assessment of percussive instrument performances with sparse coding}

% Note: Please do NOT use \thanks or a \footnote in any of the author markup

% Single address
% To use with only one author or several with the same address
% ---------------
\oneauthor
 {Names should be omitted for double-blind reviewing}
 {Affiliations should be omitted for double-blind reviewing}

%\oneauthor
%{Chih-Wei Wu, Alexander Lerch}
%{Georgia Institute of Technology, Center for Music Technology \\ \tt \{cwu307, alexander.lerch\}@gatech.edu}
 
% Two addresses
% --------------
%\twoauthors
%  {First author} {School \\ Department}
%  {Second author} {Company \\ Address}

%% To make customize author list in Creative Common license, uncomment and customize the next line
%  \def\authorname{First Author, Second Author}


% Three addresses
% --------------
%\threeauthors
%  {First Author} {Affiliation1 \\ {\tt author1@ismir.edu}}
%  {Second Author} {\bf Retain these fake authors in\\\bf submission to preserve the formatting}
%  {Third Author} {Affiliation3 \\ {\tt author3@ismir.edu}}

%% To make customize author list in Creative Common license, uncomment and customize the next line
%  \def\authorname{First Author, Second Author, Third Author}

% Four or more addresses
% OR alternative format for large number of co-authors
% ------------
%\multauthor
%{First author$^1$ \hspace{1cm} Second author$^1$ \hspace{1cm} Third author$^2$} { \bfseries{Fourth author$^3$ \hspace{1cm} Fifth author$^2$ \hspace{1cm} Sixth author$^1$}\\
%  $^1$ Department of Computer Science, University , Country\\
%$^2$ International Laboratories, City, Country\\
%$^3$  Company, Address\\
%{\tt\small CorrespondenceAuthor@ismir.edu, PossibleOtherAuthor@ismir.edu}
%}
%\def\authorname{First author, Second author, Third author, Fourth author, Fifth author, Sixth author}


\sloppy % please retain sloppy command for improved formatting

\begin{document}

%
\maketitle
%
\begin{abstract}
The automatic assessment of (student) music performance involves the characterization of the audio recordings and the modeling of human judgments. To build a computational model that provides a reliable assessment, the system must take into account various aspects of a performance including technical correctness and aesthetic standards. While some progress has been made in recent years, the search for the most effective feature representation remains open-ended. In this study, we explore the possibility of using learned features from sparse coding. Specifically, we investigate the effectiveness of different combinations of three sets of features, namely a baseline set, a set of designed features, and a learned feature set. In addition, we compare the effectiveness of sparse coding based on different input representations. The proposed feature sets are evaluated in regression tasks on a large dataset of annotated recordings of students playing snare exercises. The results imply the general viability of feature learning in the context of automatic assessment of snare drum performances.   
\end{abstract}
%
\section{Introduction}

WRITE SOMETHING HERE \cite{Author:00}

\section{Related Work}

\section{Method}

\subsection{Sparse Coding}

\subsection{Feature Learning}
% talk about two different inpu representations I tried
% STFT & IOI hist

\subsection{Regression}

\section{Experiments}

\subsection{Dataset}

\subsection{Experiment Setup}

\subsection{Metrics}

\subsection{Results and Discussion}


\section{Conclusion}


\section{References}


% For bibtex users:
\bibliography{cw_ismir2017_fba}

\end{document}
